Download, Compile and Link OpenBLAS Library with R

### 2020-12-15 README.Rmd
Update README.md.
Update README.md. Adding animated examples via the asciicast package. Updating site.

   - As stated earlier, the procedure works for any Linux and this includes Android. If your Android is capable of running privileged commands (ROOT) and if you have [**R**](https://www.r-project.org/) installed via Termux with the required dependencies, you can compile and link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) using ropenblas;

@@

```
devtools::install_github(repo = "prdm0/ropenblas", force = TRUE)
```

@@

**Note**: If you want to access the latest features of the [**ropenblas**](https://prdm0.github.io/ropenblas/) package, install it using the first procedure.

@@

Installing, compiling, and linking the [**OpenBLAS**](https://www.openblas.net/) version **0.3.12** library to the [**R**](https://www.r-project.org/) language:

```
ropenblas(x = "0.3.12")
```

**Notes**:

   - You do not have to in every section of [**R**](https://www.r-project.org/) make use of the `ropenblas()` function. Once the function is used, [**R**](https://www.r-project.org/) will always consider using the [**OpenBLAS**](https://www.openblas.net/) library in future sections.

   - [**OpenBLAS**](https://www.openblas.net/) versions tested: 0.3.0, 0.3.1, 0.3.2, 0.3.3, 0.3.4, 0.3.5, 0.3.6, 0.3.7, 0.3.8, 0.3.9, 0.3.10, 0.3.11 and 0.3.12. These are the values that will be passed to `x` in `ropenblas(x)`;

   - If `x = NULL`, the latest stable version of the [**OpenBLAS**](https://www.openblas.net/) library will be compiled and linked to [**R**](https://www.r-project.org/).

**Details**

Your linux operating system may already be configured to use the [**OpenBLAS**](https://www.openblas.net/) library. Therefore, most likely [**R**](https://www.r-project.org/) will already be linked to this library. To find out if the [**R**](https://www.r-project.org/) language is using the [**OpenBLAS**](https://www.openblas.net/) library, at [**R**](https://www.r-project.org/), do:

```
extSoftVersion()["BLAS"]
```

If [**R**](https://www.r-project.org/) is using the [**OpenBLAS**](https://www.openblas.net/) library, something like `/any_directory/libopenblas.so` should be returned. Therefore, there should be the name **openblas** in the **s**hared **o**bject returned (file extension **.so**).

If the `ropenblas()` function can identify that the [**R**](https://www.r-project.org/) language is using the version of [**OpenBLAS**](https://www.openblas.net/) you wish to configure, a warning message will be returned asking if you really would like to proceed with the configuration again.

The `ropenblas()` function will download the desired version of the library [**OpenBLAS**](https://www.openblas.net/), compile and install the library in the `/opt` directory of your operational system. If the directory does not exist, it will be created so that the installation can be completed. Subsequently, files from the version of [**BLAS**](http://www.netlib.org/blas/) used in [**R**](https://www.r-project.org/) will be symbolically linked to the shared object files of the library version [**OpenBLAS**](https://www.openblas.net/) compiled and installed in `/opt`.

You must be the operating system administrator to use this library. Therefore, do not attempt to use it without telling your system administrator. If you have the ROOT password, you will be responsible for everything you do on your operating system.

You will not necessarily have to run `ropenblas()` on every section of [**R**](https://www.r-project.org/). Almost always it will not be necessary. However, it may be that the [**R**](https://www.r-project.org/) is updated by the operating system (GNU/Linux). Thus, it may be that in this update the [**R**](https://www.r-project.org/) unlink with the [**OpenBLAS**](https://www.openblas.net/) library. Therefore, from time to time check using the command `extSoftVersion()["BLAS"]` if the link with [**OpenBLAS**](https://www.openblas.net/) is correct, otherwise run the command `ropenblas()` again.

@@

```
> last_version_r()
$last_version
[1] "4.0.3"

$versions
[1] "4.0.0" "4.0.1" "4.0.2" "4.0.3"

$n
[1] 4
```

```
> last_version_r(major = 3L)
$last_version
[1] "3.6.3"

$versions
 [1] "3.0.0"         "3.0.1"         "3.0.2"         "3.0.3"         "3.1.0"         "3.1.1"         "3.1.2"         "3.1.3"        
 [9] "3.2.0"         "3.2.1"         "3.2.2"         "3.2.3"         "3.2.4-revised" "3.2.4"         "3.2.5"         "3.3.0"        
[17] "3.3.1"         "3.3.2"         "3.3.3"         "3.4.0"         "3.4.1"         "3.4.2"         "3.4.3"         "3.4.4"        
[25] "3.5.0"         "3.5.1"         "3.5.2"         "3.5.3"         "3.6.0"         "3.6.1"         "3.6.2"         "3.6.3"

$n
[1] 32
```

**Note**: If `major = NULL`, the function will consider the major release number.

@@

```
> last_version_openblas()
$last_version
[1] "0.3.12"

$versions
 [1] "0.1alpha1"   "0.1alpha2"   "0.1alpha2.1" "0.1alpha2.2" "0.1alpha2.3" "0.1alpha2.4" "0.1alpha2.5" "0.1.0"      
 [9] "0.1.1"       "0.2.0"       "0.2.1"       "0.2.2"       "0.2.3"       "0.2.4"       "0.2.5"       "0.2.6"      
[17] "0.2.7"       "0.2.8"       "0.2.9"       "0.2.9.rc1"   "0.2.9.rc2"   "0.2.10"      "0.2.10.rc1"  "0.2.10.rc2" 
[25] "0.2.11"      "0.2.12"      "0.2.13"      "0.2.14"      "0.2.15"      "0.2.16"      "0.2.16.rc1"  "0.2.17"     
[33] "0.2.18"      "0.2.19"      "0.2.20"      "0.3.0"       "0.3.1"       "0.3.2"       "0.3.3"       "0.3.4"      
[41] "0.3.5"       "0.3.6"       "0.3.7"       "0.3.8"       "0.3.9"       "0.3.10"      "0.3.11"      "0.3.12"

$n
[1] 48
```

@@

```
rcompiler()
```

@@

In addition to the `x` argument, the` rcompiler()` function has two other arguments that will allow you to change and pass new compilation flags. Are they:

1. `with_blas`: This argument sets the `--with-blas` flag in the R language compilation process and must be passed as a string. Details on the use of this flag can be found [**here**](https://cran.r-project.org/doc/manuals/r-devel/R-admin.html). If `with_blas = NULL` (default), then it will be considered:

   ```
   ./configure --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib --enable-threads=posix
   --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm"
   ```

   Most likely, you will have little reason to change this argument. Unless you know what you're doing, consider `with_blas = NULL`. Do not change the installation directory, that is, always consider `--prefix = /opt/R/version_r`, where` version_r` is a valid version of [**R**](https://www.r-project.org/). For a list of valid versions of [**R**](https://www.r-project.org/), run the `last_version_r()`.
Installing [**R**](https://www.r-project.org/) in the `/opt/R/version_r` directory is important because some functions in the package require this. Both the [**R**](https://www.r-project.org/) language and the [**OpenBLAS**](https://www.openblas.net/) library will be installed in the `/opt` directory. If this directory does not exist in your GNU/Linux distribution, it will be created;

2. `complementary_flags`: String (`complementary_flags = NULL` by default) for adding complementary flags in the [**R**](https://www.r-project.org/) language compilation process. Passing a string to `complementary_flags` will compile it in the form:

   ```
    ./configure --with-blas="..." complementary_flags
   ```

@@

```
link_again()
```

>>>>

   <!-- - As stated earlier, the procedure works for any Linux and this includes Android. If your Android is capable of running privileged commands (ROOT) and if you have [**R**](https://www.r-project.org/) installed via Termux with the required dependencies, you can compile and link [**OpenBLAS**](https://www.openblas.net/) with [**R**](https://www.r-project.org/) using ropenblas; -->

@@

```
remotes::install_github(repo = "prdm0/ropenblas", force = TRUE)
```

@@

<!-- **Note**: If you want to access the latest features of the [**ropenblas**](https://prdm0.github.io/ropenblas/) package, install it using the first procedure. -->

@@

Installing, compiling, and linking the [**OpenBLAS**](https://www.openblas.net/) version **0.3.13** library to the [**R**](https://www.r-project.org/) language:

```{r, fig.align='center',  echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/ropenblas.svg")
```

<!-- **Notes**:  -->

<!--    - You do not have to in every section of [**R**](https://www.r-project.org/) make use of the `ropenblas()` function. Once the function is used, [**R**](https://www.r-project.org/) will always consider using the [**OpenBLAS**](https://www.openblas.net/) library in future sections. -->

<!--    - [**OpenBLAS**](https://www.openblas.net/) versions tested: 0.3.0, 0.3.1, 0.3.2, 0.3.3, 0.3.4, 0.3.5, 0.3.6, 0.3.7, 0.3.8, 0.3.9, 0.3.10, 0.3.11, 0.3.12 and 0.3.13. These are the values that will be passed to `x` in `ropenblas(x)`;  -->

<!--    - If `x = NULL`, the latest stable version of the [**OpenBLAS**](https://www.openblas.net/) library will be compiled and linked to [**R**](https://www.r-project.org/). -->

<!-- **Details** -->

<!-- Your linux operating system may already be configured to use the [**OpenBLAS**](https://www.openblas.net/) library. Therefore, most likely [**R**](https://www.r-project.org/) will already be linked to this library. To find out if the [**R**](https://www.r-project.org/) language is using the [**OpenBLAS**](https://www.openblas.net/) library, at [**R**](https://www.r-project.org/), do: -->

<!-- ``` -->
<!-- extSoftVersion()["BLAS"] -->
<!-- ``` -->

<!-- If [**R**](https://www.r-project.org/) is using the [**OpenBLAS**](https://www.openblas.net/) library, something like `/any_directory/libopenblas.so` should be returned. Therefore, there should be the name **openblas** in the **s**hared **o**bject returned (file extension **.so**). -->

<!-- If the `ropenblas()` function can identify that the [**R**](https://www.r-project.org/) language is using the version of [**OpenBLAS**](https://www.openblas.net/) you wish to configure, a warning message will be returned asking if you really would like to proceed with the configuration again. -->

<!-- The `ropenblas()` function will download the desired version of the library [**OpenBLAS**](https://www.openblas.net/), compile and install the library in the `/opt` directory of your operational system. If the directory does not exist, it will be created so that the installation can be completed. Subsequently, files from the version of [**BLAS**](http://www.netlib.org/blas/) used in [**R**](https://www.r-project.org/) will be symbolically linked to the shared object files of the library version [**OpenBLAS**](https://www.openblas.net/) compiled and installed in `/opt`. -->

<!-- You must be the operating system administrator to use this library. Therefore, do not attempt to use it without telling your system administrator. If you have the ROOT password, you will be responsible for everything you do on your operating system. -->

<!-- You will not necessarily have to run `ropenblas()` on every section of [**R**](https://www.r-project.org/). Almost always it will not be necessary. However, it may be that the [**R**](https://www.r-project.org/) is updated by the operating system (GNU/Linux). Thus, it may be that in this update the [**R**](https://www.r-project.org/) unlink with the [**OpenBLAS**](https://www.openblas.net/) library. Therefore, from time to time check using the command `extSoftVersion()["BLAS"]` if the link with [**OpenBLAS**](https://www.openblas.net/) is correct, otherwise run the command `ropenblas()` again. -->

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/last_version_r.svg")
```

<!-- **Note**: If `major = NULL`, the function will consider the major release number. -->

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/last_version_openblas.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/rcompiler.svg")
```

@@

<!-- In addition to the `x` argument, the` rcompiler()` function has two other arguments that will allow you to change and pass new compilation flags. Are they: -->

<!-- 1. `with_blas`: This argument sets the `--with-blas` flag in the R language compilation process and must be passed as a string. Details on the use of this flag can be found [**here**](https://cran.r-project.org/doc/manuals/r-devel/R-admin.html). If `with_blas = NULL` (default), then it will be considered: -->

<!--    ``` -->
<!--    ./configure --prefix=/opt/R/version_r --enable-memory-profiling --enable-R-shlib --enable-threads=posix -->
<!--    --with-blas="-L/opt/OpenBLAS/lib -I/opt/OpenBLAS/include -lpthread -lm" -->
<!--    ``` -->

<!--    Most likely, you will have little reason to change this argument. Unless you know what you're doing, consider `with_blas = NULL`. Do not change the installation directory, that is, always consider `--prefix = /opt/R/version_r`, where` version_r` is a valid version of [**R**](https://www.r-project.org/). For a list of valid versions of [**R**](https://www.r-project.org/), run the `last_version_r()`. -->
<!-- Installing [**R**](https://www.r-project.org/) in the `/opt/R/version_r` directory is important because some functions in the package require this. Both the [**R**](https://www.r-project.org/) language and the [**OpenBLAS**](https://www.openblas.net/) library will be installed in the `/opt` directory. If this directory does not exist in your GNU/Linux distribution, it will be created; -->

<!-- 2. `complementary_flags`: String (`complementary_flags = NULL` by default) for adding complementary flags in the [**R**](https://www.r-project.org/) language compilation process. Passing a string to `complementary_flags` will compile it in the form: -->

<!--    ``` -->
<!--     ./configure --with-blas="..." complementary_flags -->
<!--    ``` -->

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/link_again.svg")
```
